What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-06-27 android-stacks.tex
changing the focus of Introduction

In this work, we perform the first large scale analysis of Java stack traces and
pinpoint how they can reveal bad programming practices. We mined and analyzed
the stack traces embedded in all issues of Java projects available GitHub.
Overall, our research set includes 356,057 issues defined at 16,836 projects, 
from which 28,800 stack traces were extracted. From this set, the stack traces
of 482 Android projects were investigated in more detail, in combination with
source code and bytecode analysis. In this study some patterns of exception
(mis)-use were consistently detected such as: unexpected wrappings (e.g., Errors
being wrapped in checked exceptions), revealing that Java hybrid exception
model is not fully used according to its purpose;  undocumented runtime
exceptions signaled by third party code, which is a serious threat to program
dependability; and a high prevalence of java.lang exceptions reported on issues,  
causing approximately 50\% of the analyzed stack traces.

@@

@@

In Java, when the program fails due to an uncaught exception, it automatically
terminates, while the system prints a stack trace to the console. A stack trace
includes an explanatory message and the execution stack frame when the exception
occurred. A typical Java stack trace consists of an ordered list of methods that
were active on the call stack before the exception occurred. Stack traces
are a useful source of information about system crashes, and are often used to
support developers in debugging~\cite{schroter2010stack}. Moreover, information
from stack traces combined with crash and bug reports can be used to support bug
classification and clustering~\cite{wang2013improving, kim2011crash,
dhaliwal2011classifying}, fault-proneness prediction
models~\cite{kim2013predicting} and even automated bug
fixing~\cite{sinha2009fault} tools.

>>>>

In this work, we perform the first large scale analysis of Java stack traces and
pinpoint how they can reveal bad programming practices. We mined and analyzed
the stack traces embedded in all issues of Java projects available GitHub.
Overall, our research set includes 356,057 issues defined at 16,836 projects, 
from which 28,800 stack traces were extracted. From this set, the stack traces
of 482 Android projects were investigated in more detail, in combination with
source code and bytecode analysis. In this study some patterns of exception
(mis)-use were consistently detected such as: unexpected wrappings (e.g., Errors
being wrapped in checked exceptions), revealing that Java hybrid exception
model is not fully used according to its purpose;  undocumented runtime
exceptions signaled by third party code, which is a serious threat to program
dependability; and a high prevalence of java.lang exceptions reported on issues,  
they were found in aproximately 50\% of all analyzed exception stack traces.

@@

Along the recent years we have witnessed a rapid increase in 
the number of open source software (oss) available on the Web.
Since such projects make their control version system, mailing lists and 
bug tracking systems (bts) publicly available, they represent a valuable 
source of information for the "state of practice" on software development
which has already started to be investigated [][][][][].

In this scenario Github emerged as one of the most used repository hosting sites.
It  alows developers to create and maintain opensource projects relying on Git distributed version 
control and provides a set of tools which allow the information about developers 
and their activities to be visible within and across open souce projects.

Github is also known as a social coding platfotm [ref] as it ....

Among those tools there is the Github issue tracking system, which makes
issues related to new, features, bugs and general comments publicly available.

The bug issues have been the focus of some research... In [ref] defined a 
set of characteristics a good bug issue should have. The 2 most important information 
are the: (1) steps to reproduce the bug; (2) and the failure stack trace.

A typical stack trace consists of an ordered list of methods that
were active on the call stack before the failure occurred. Stack traces
are a useful source of information about system crashes, and are often used to
support developers in debugging~\cite{schroter2010stack}. Moreover, information
from stack traces combined with crash and bug reports can be used to support bug
classification and clustering~\cite{wang2013improving, kim2011crash,
dhaliwal2011classifying}, fault-proneness prediction
models~\cite{kim2013predicting} and even automated bug
fixing~\cite{sinha2009fault} tools.

However, all existing research has focused on the analysis of a single system at a time. In
our current context, on which we have access to wealth of information available
on open-source repositories like GitHub additional questions arise: What are the common
characteristics of such stack traces? Can developers benefit from other systems faults?

-----
Along the recent years we have witnessed a rapid increase in 
the number of social applications on the Web. Applications which 
allow their users to track the activities of a large number 
of others regardless of his/her location and affiliation.

This tendency can also be seen on the software development context 
where Github emerged and became an extensively used social coding 
platform. Github alows developers to create and maintain opensource 
projects relying  on Git distributed version control, and provides a set 
of tools which allow the information about developers and their activities
 to be visible within and across open souce projects.

Among those tools there is the Github issue tracking system, which makes
issues related to new, features, bugs and general comments publicly available.

-----

@@

In Java, when the program fails due to an uncaught exception, it automatically
terminates, while the system prints a stack trace to the console.

A stack trace
includes an explanatory message and the execution stack frame when the exception
occurred. A typical Java stack trace consists of an ordered list of methods that
were active on the call stack before the exception occurred. Stack traces
are a useful source of information about system crashes, and are often used to
support developers in debugging~\cite{schroter2010stack}. Moreover, information
from stack traces combined with crash and bug reports can be used to support bug
classification and clustering~\cite{wang2013improving, kim2011crash,
dhaliwal2011classifying}, fault-proneness prediction
models~\cite{kim2013predicting} and even automated bug
fixing~\cite{sinha2009fault} tools.
